### 2015-07-13 narrative/data-reduction.tex
small wording changes

To implement these plugin capabilities, we will build upon our existing data staging 
capability and further allow data to be
efficiently staged, re-organized and mapped to a multi-tiered storage. Various
processing scenarios such as in-situ, in-transit or a combination of the two
will be researched and developed to meet our needs.
%The open questions that will be addressed include: 
%1) do we move the data over to
%other nodes to then reduce and re-organize, 2) do we first reduce the data and
%then later re-organize this data on different nodes?, or 3) do we use different
%cores on a node to do data-refactoring.  
Similarly we will examine the cost of reading the data. In the case where only high importance being retrieved,
overall time to move the data from SIRUS to the
application is expected to fast. A key challenge is in the assessment of retrieving
both high and low important data that reside across storage tiers and possibly migrate to
new locations as a result of capacity pressure. There is a
clear penalty of having to discovery data (\S\ref{sec:naming-discovery}), take data in a hierarchical layout and then re-compose
this back to a single-layer view.  
%Additional research questions which must be
%addressed: Will some types of data (e.g. PIC data) be more
%conducive  for data-refactoring than others? How much semantic-domain knowledge
%will we need to get a dramatic improvement of the storage system over not doing
%anything special?

>>>>

To implement these plug-in capabilities, we will build upon our existing data staging 
capability and further allow data to be
efficiently staged, re-organized and mapped to a multi-tiered storage. Various
processing scenarios such as in-situ, in-transit or a combination of the two
will be researched and developed to meet our needs.
%The open questions that will be addressed include: 
%1) do we move the data over to
%other nodes to then reduce and re-organize, 2) do we first reduce the data and
%then later re-organize this data on different nodes?, or 3) do we use different
%cores on a node to do data-refactoring.  
Similarly we will examine the cost of reading the data. In the case where only high importance being retrieved,
overall time to move the data from SIRUS to the
application is expected to fast. A key challenge is in the assessment of retrieving
both high and low important data that reside across storage tiers and possibly migrate to
new locations as a result of capacity pressure. There is a
clear penalty of having to discovery data (\S\ref{sec:naming-discovery}), take data in a hierarchical layout and then re-compose
this back to a single-layer view.  
%Additional research questions which must be
%addressed: Will some types of data (e.g. PIC data) be more
%conducive  for data-refactoring than others? How much semantic-domain knowledge
%will we need to get a dramatic improvement of the storage system over not doing
%anything special?

### 2015-07-13 narrative/intro.tex
small wording changes

\begin{table}[htbp]
\small
\vspace{2ex}
\begin{center}
\caption {Relevance to SSIO}
\label{tab:call}
\begin{tabular}{ | p {0.2cm} | p{5cm} | p{7.5cm} | p{2.2cm} |}\hline
\multicolumn{2}{|c|}{\bf Call area} & \multicolumn{1}{|c|}{\bf Relevant S2E2 work} & \multicolumn{1}{|c|}{\bf Proposed research} \\\hline\hline
1 & Data abstractions & Create new APIs  and annotations to guide data placement across the storage system & \S\ref{sec:data-description} \\\hline
2 & Mapping science data models onto hierarchical storage &  Enable science-driven mapping, re-organization, reduction and prioritization of data chunks derive from application objects & \S\ref{sec:data-refactor}, \S\ref{sec:data-description},  \S\ref{sec:managing-data-life}\\\hline
3 & Mechanisms for data movement across the storage hierarchy & Enable science-driven data placement and migration based on policies& \S \ref{sec:managing-data-life},  \S\ref{sec:migration} \\\hline
4 &  Extend the interaction of middleware with the storage system & Manage data placement and migration between the application, middleware and storage system using an autonomic cross-layer approach & \S\ref{sec:managing-data-life}, \S\ref{sec:qos}, \S\ref{sec:naming-discovery}  \\\hline
5 & Design and implement of I/O middleware architectures  & Create APIs to guide the placement of chunks of data across the SSIO and autonomically move data& \S\ref{sec:data-description}, \S\ref{sec:managing-data-life}, \S\ref{sec:qos}, \S\ref{sec:naming-discovery} \\ \hline
6 &Approaches to improve the ability of SSIO software to support checkpoint/restart &  We will have utility functions defined for the lifetime of data, and allow CR data to be automatically placed in the fastest storage and then later purged & \S\ref{sec:data-description}, \S\ref{sec:managing-data-life}, \S\ref{sec:qos}, \S\ref{sec:data-description} \\ \hline
\end{tabular}
\end{center}
\vskip -0.5cm
\end{table}

>>>>

\begin{table}[htbp]
\small
\vspace{2ex}
\begin{center}
\caption {Relevance to SSIO}
\label{tab:call}
\begin{tabular}{ | p {0.2cm} | p{5cm} | p{7.5cm} | p{2.2cm} |}\hline
\multicolumn{2}{|c|}{\bf Call area} & \multicolumn{1}{|c|}{\bf Relevant SIRIUS work} & \multicolumn{1}{|c|}{\bf Proposed research} \\\hline\hline
1 & Data abstractions & Create new APIs  and annotations to guide data placement across the storage system & \S\ref{sec:data-description} \\\hline
2 & Mapping science data models onto hierarchical storage &  Enable science-driven mapping, re-organization, reduction and prioritization of data chunks derive from application objects & \S\ref{sec:data-refactor}, \S\ref{sec:data-description},  \S\ref{sec:managing-data-life}\\\hline
3 & Mechanisms for data movement across the storage hierarchy & Enable science-driven data placement and migration based on policies& \S \ref{sec:managing-data-life},  \S\ref{sec:migration} \\\hline
4 &  Extend the interaction of middleware with the storage system & Manage data placement and migration between the application, middleware and storage system using an autonomic cross-layer approach & \S\ref{sec:managing-data-life}, \S\ref{sec:qos}, \S\ref{sec:naming-discovery}  \\\hline
5 & Design and implement of I/O middleware architectures  & Create APIs to guide the placement of chunks of data across the SSIO and autonomically move data& \S\ref{sec:data-description}, \S\ref{sec:managing-data-life}, \S\ref{sec:qos}, \S\ref{sec:naming-discovery} \\ \hline
6 &Approaches to improve the ability of SSIO software to support checkpoint/restart &  We will have utility functions defined for the lifetime of data, and allow CR data to be automatically placed in the fastest storage and then later purged & \S\ref{sec:data-description}, \S\ref{sec:managing-data-life}, \S\ref{sec:qos}, \S\ref{sec:data-description} \\ \hline
\end{tabular}
\end{center}
\vskip -0.5cm
\end{table}

### 2015-07-13 narrative/proposed-work.tex
small wording changes

We propose to overcome these challenges by pioneering a new {\bf
knowledge-centric approach} to a dynamic storage system and I/O layer which
takes into account user prioritization and utility to optimize the SSIO layer.
The approach is based on two underlying principles:

@@

\underline{Principle 2}: {\bf Predictable performance and quality of data in the SSIO layers} needs to be
established so science can be done on the exascale systems in a more efficient manner. Without
predictable performance, not only can the runs be slowed down because of contentions \cite{liu_hotstorage}, 
but also it affects key science decisions, e.g., how much data reduction should be performed.
It is clear that if a run is expected to be slow, an aggresive data reduction needs to be performed
so that science can be done in a timely fashion, which has been reflected in the XGC run (\S~\ref{sec:introduction})
that the PI recently participated.

We aim to alleviate the need for the ``magic'' and ``tricks''
that are currently required to optimize application I/O performance
on today's file systems. To accomplish this, we will provide a systematic
approach for describing intentions and other knowledge from {\it user}
space, as well as allow performance estimations and guarantees 
from the underlyingree storage.
%For example, ADIOS contains most of the ``best practices'' for I/O optimizations for
%   each file system, and as users place more knowledge into ADIOS, ADIOS
%   can make optimizations.
By capturing user intentions and acting upon them in the middleware, we
free the user from polluting application code with system specific
optimizations which may provide better performance in the short term,
but are detrimental to the long-term maintainability of applications, and
are more sensitive to changes to system configuration. We have successfully
employed this strategy of separation of concerns in ADIOS, and believe that
it will become increasingly important because saving all data may not be possible, and
users want the ability to describe and prioritize different chunks of data. 
Our research is aimed to allow users to provide simple descriptions of their data,
which further allows the middleware and storage to optimize application I/O performance.

Additionally we recognize that HPC applications exhibit a set
of common I/O patterns \cite{lofstead2011six,polte2009and,tian2011edo,tian2012system}.
Throughout our project we will continuously focus on creating research artifacts 
which can optimize these I/O patterns on current and
exascale systems. One key focus is Checkpoint/Restart (C/R), leveraging NVRAM to accelerate
checkpoint and data retrieval. 
The migration and purging of this will be optimized by SIRUS using the utility function of 
the C/R data so that this can be stored for short periods of time, and then purged.

>>>>

We propose to overcome the challenges described earlier by pioneering a new {\bf
knowledge-centric approach} to a dynamic storage system and I/O layer which
optimize the SSIO layer on the following two principles:
% The approach is based on two underlying principles:

@@

\underline{Principle 2}: {\bf Predictable performance and quality of data in the SSIO layers} needs to be
established so science can be done on the exascale systems in a more efficient manner. Without
predictable performance, not only can the runs be slowed down because of
shared resource contention \cite{liu_hotstorage,lofstead2010managing}, 
but also it affects key science decisions, e.g., how much data reduction should be performed.
% It is clear that if a run is expected to be slow, an aggresive data reduction needs to be performed
% so that science can be done in a timely fashion, which has been reflected in the XGC run (\S~\ref{sec:introduction})
% that the PI recently participated.

We aim to alleviate the need for the ``magic'' and ``tricks''
that are currently required to optimize application I/O performance
on today's file systems. To accomplish this, we will provide a systematic
approach for describing intentions and other knowledge from the {\it user}, 
as well as allow performance estimations and guarantees 
from the underlying storage.
%For example, ADIOS contains most of the ``best practices'' for I/O optimizations for
%   each file system, and as users place more knowledge into ADIOS, ADIOS
%   can make optimizations.
By capturing user intentions and acting upon them in the middleware, we
free the user from polluting application code with system specific
optimizations which may provide better performance in the short term,
but are detrimental to the long-term maintainability of applications, and
are more sensitive to changes in the system configuration. We have successfully
employed this strategy of separation of concerns in ADIOS, and believe that
it will become increasingly important because saving all data may not be possible, and
users want the ability to describe and prioritize different chunks of data. 
Our research is aimed to allow users to provide simple descriptions of their data,
which further allows the middleware and storage to optimize application I/O performance.

Additionally we recognize that HPC applications exhibit a set
of common I/O patterns \cite{lofstead2011six,polte2009and,tian2011edo,tian2012system}.
Throughout our project we will continuously focus on creating research artifacts 
which can optimize these I/O patterns on current and
exascale systems. One area of focus is Checkpoint/Restart (C/R), leveraging NVRAM to accelerate
checkpoint and data retrieval. 
The migration and purging of this will be optimized by SIRUS using the utility function of 
the C/R data so that this can be stored for short periods of time, and then purged.
